---
title: "FML ASSIGNMENT 1"
output:
  pdf_document: default
  html_document: default
  word_document: default
date: "2024-02-04"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Source of my Dataset:


```{r}
library(readr)
HeartFailure_Prediction<-
read.csv("C:/Users/deeks/Downloads/heart.csv")
View(HeartFailure_Prediction)
```

#The descriptive statistics for the dataset:

```{r}
summary(HeartFailure_Prediction)
```

#The Qualitative Variables are:

```{r}
summary(HeartFailure_Prediction$Sex)
```

```{r}
summary(HeartFailure_Prediction$ChestPainType)
```
```{r}
summary(HeartFailure_Prediction$RestingECG)
```

```{r}
summary(HeartFailure_Prediction$ExerciseAngina)
```
```{r}
summary(HeartFailure_Prediction$ST_Slope)
```

#The Quantitative variables are"

```{r}
summary(HeartFailure_Prediction$Age)
```

```{r}
summary(HeartFailure_Prediction$RestingBP)
```
```{r}
summary(HeartFailure_Prediction$Cholesterol)
```
```{r}
summary(HeartFailure_Prediction$FastingBS)
```

```{r}
summary(HeartFailure_Prediction$MaxHR)
```

```{r}
summary(HeartFailure_Prediction$Oldpeak)
```

```{r}
summary(HeartFailure_Prediction$HeartDisease)
```
#MEAN OF CHOLESTROL

```{r}
mean(HeartFailure_Prediction$Cholesterol)
```
#MEDIAN OF CHOLESTROL

```{r}
median(HeartFailure_Prediction$Cholesterol)
```
#MODE OF CHOLESTROL

```{r}
mode<-function(x){
  n<-table(HeartFailure_Prediction$Cholesterol)
  which.max(n)
}
mode(HeartFailure_Prediction$Cholesterol)
```

#DESCRIPTIVE STATISTICS FOR A CATEGORIAL VARIABLE

```{r}
table(HeartFailure_Prediction$Sex)
```
#TRANSFORMATION OF HEART FAILURE PREDICTION OF DATASET

```{r}
transform(HeartFailure_Prediction$Oldpeak+ 1)
```

#CREATING A SCATTERPLOT FOR HEART FAILURE PREDICTION DATASET

```{r}
x=HeartFailure_Prediction$Age
y=HeartFailure_Prediction$RestingBP
plot(x,y,main = "AGE Vs RESTINGBP" ,xlab = "Age",ylab = "RestingsBP")
```


